`r params$doc_title`

### 2023-05-09 scripts/MSc.Rmd
updated tables, highlighting best methods

```{r parallel-performance, warning=FALSE}
for (true_method in 1:length(selected_true_methods)) {
  # define reference estimate for ALL 5 chosen methods in loop 
  args.gsd.method <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == selected_true_methods[true_method]], 
                          nsim=nrow(est_sim)
  )
  #1
  IVW_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, IVW_GSD_mean=mean, IVW_GSD_emp_se=emp_se, IVW_GSD_bias=bias, IVW_GSD_mse=mse)
  #2
  MODE_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_MODE_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, MODE_GSD_mean=mean, MODE_GSD_emp_se=emp_se, MODE_GSD_bias=bias, MODE_GSD_mse=mse)
  #3
  CONMIX_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_CONMIX_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, CONMIX_GSD_mean=mean, CONMIX_GSD_emp_se=emp_se, CONMIX_GSD_bias=bias, CONMIX_GSD_mse=mse)
  #4
  MRMIX_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_MRMIX_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, MRMIX_GSD_mean=mean, MRMIX_GSD_emp_se=emp_se, MRMIX_GSD_bias=bias, MRMIX_GSD_mse=mse)
  #5
  MEDIAN_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_MEDIAN_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, MEDIAN_GSD_mean=mean, MEDIAN_GSD_emp_se=emp_se, MEDIAN_GSD_bias=bias, MEDIAN_GSD_mse=mse)
  #6
  EGGER_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_EGGER_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, EGGER_GSD_mean=mean, EGGER_GSD_emp_se=emp_se, EGGER_GSD_bias=bias, EGGER_GSD_mse=mse)
  #7
  ROBUST_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_ROBUST_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, ROBUST_GSD_mean=mean, ROBUST_GSD_emp_se=emp_se, ROBUST_GSD_bias=bias, ROBUST_GSD_mse=mse)
  #8
  PRESSO_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_PRESSO_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, PRESSO_GSD_mean=mean, PRESSO_GSD_emp_se=emp_se, PRESSO_GSD_bias=bias, PRESSO_GSD_mse=mse)
  #9
  RAPS_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_RAPS_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, RAPS_GSD_mean=mean, RAPS_GSD_emp_se=emp_se, RAPS_GSD_bias=bias, RAPS_GSD_mse=mse)
  #10
  LASSO_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_LASSO_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, LASSO_GSD_mean=mean, LASSO_GSD_emp_se=emp_se, LASSO_GSD_bias=bias, LASSO_GSD_mse=mse)

@@

  ###
  ## PLOT  -------------------------------------------------------------------
  ###
  IVW_BMI_GSD_geom_point_dat <- est_sim %>% 
    select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
    pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
    mutate(theta_sim_numeric = as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")))

  ggplot(IVW_GSD_performance_metrics, aes(x=N, y=IVW_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
    # geom_errorbar(aes(ymin=IVW_GSD_mean-1.96*IVW_GSD_emp_se, ymax=IVW_GSD_mean+1.96*IVW_GSD_emp_se), 
    #               width=3000, # x-axis dimension
    #               position = "dodge")+
    ## ADD rainbow plots
    geom_boxplot(data = IVW_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = IVW_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = IVW_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("IVW estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
                           ))+
    theme_few() -> IVW_GSD_simplot_thetas

@@

  ggplot(MODE_GSD_performance_metrics, aes(x=N, y=MODE_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
    # geom_errorbar(aes(ymin=MODE_GSD_mean-1.96*MODE_GSD_emp_se, ymax=MODE_GSD_mean+1.96*MODE_GSD_emp_se), 
    #               width=3000, # x-axis dimension
    #               position = "dodge")+
    ## ADD rainbow plots
    geom_boxplot(data = MODE_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = MODE_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = MODE_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("MODE estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
         )
    ) +
    theme_few() -> MODE_GSD_simplot_thetas

@@

  ggplot(CONMIX_GSD_performance_metrics, aes(x=N, y=CONMIX_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
    ## ADD rainbow plots
    geom_boxplot(data = CONMIX_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = CONMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = CONMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("CONMIX estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
         )
    ) +
    theme_few() -> CONMIX_GSD_simplot_thetas

@@

  ggplot(MRMIX_GSD_performance_metrics, aes(x=N, y=MRMIX_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
    ## ADD rainbow plots
    geom_boxplot(data = MRMIX_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = MRMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = MRMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("MRMIX estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
         )
    ) +
    theme_few() -> MRMIX_GSD_simplot_thetas

@@

  ggplot(MEDIAN_GSD_performance_metrics, aes(x=N, y=MEDIAN_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
    ## ADD rainbow plots
    geom_boxplot(data = MEDIAN_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = MEDIAN_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = MEDIAN_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("MEDIAN estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
         )
    ) +
    theme_few() -> MEDIAN_GSD_simplot_thetas

@@

  if (SAVE.files ==TRUE ){
    filename_GSD_simplot_thetas_arrange <- paste0("./output/plots/theta_sims/", Sys.Date(), "_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".svg")
    ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
           width = 10, height = 38, device = "svg",
           units = "in"  # default
           )
  }

@@

>>>>

```{r parallel-performance, warning=FALSE}

arrangedplot.thetas.all <- list()

for (true_method in 1:length(selected_true_methods)) {
  # define reference estimate for ALL 5 chosen methods in loop 
  args.gsd.method <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == selected_true_methods[true_method]], 
                          nsim=nrow(est_sim)
  )
  #1
  IVW_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, IVW_GSD_mean=mean, IVW_GSD_emp_se=emp_se, IVW_GSD_bias=bias, IVW_GSD_mse=mse)
  #2
  MODE_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_MODE_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, MODE_GSD_mean=mean, MODE_GSD_emp_se=emp_se, MODE_GSD_bias=bias, MODE_GSD_mse=mse)
  #3
  CONMIX_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_CONMIX_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, CONMIX_GSD_mean=mean, CONMIX_GSD_emp_se=emp_se, CONMIX_GSD_bias=bias, CONMIX_GSD_mse=mse)
  #4
  MRMIX_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_MRMIX_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, MRMIX_GSD_mean=mean, MRMIX_GSD_emp_se=emp_se, MRMIX_GSD_bias=bias, MRMIX_GSD_mse=mse)
  #5
  MEDIAN_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_MEDIAN_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, MEDIAN_GSD_mean=mean, MEDIAN_GSD_emp_se=emp_se, MEDIAN_GSD_bias=bias, MEDIAN_GSD_mse=mse)
  #6
  EGGER_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_EGGER_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, EGGER_GSD_mean=mean, EGGER_GSD_emp_se=emp_se, EGGER_GSD_bias=bias, EGGER_GSD_mse=mse)
  #7
  ROBUST_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_ROBUST_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, ROBUST_GSD_mean=mean, ROBUST_GSD_emp_se=emp_se, ROBUST_GSD_bias=bias, ROBUST_GSD_mse=mse)
  #8
  PRESSO_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_PRESSO_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, PRESSO_GSD_mean=mean, PRESSO_GSD_emp_se=emp_se, PRESSO_GSD_bias=bias, PRESSO_GSD_mse=mse)
  #9
  RAPS_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_RAPS_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, RAPS_GSD_mean=mean, RAPS_GSD_emp_se=emp_se, RAPS_GSD_bias=bias, RAPS_GSD_mse=mse)
  #10
  LASSO_GSD_performance_metrics <- est_sim %>% 
    select(!!!(colname_LASSO_theta_sim_BMI_GSD)) %>% 
    map_df(.f = ~ funs %>% 
             map(exec, .x, !!!args.gsd.method), .id = "var") %>% 
    cbind(sample_size_filtered) %>% 
    rename(N = sample_size_filtered, LASSO_GSD_mean=mean, LASSO_GSD_emp_se=emp_se, LASSO_GSD_bias=bias, LASSO_GSD_mse=mse)

@@

  ###
  ## PLOT  -------------------------------------------------------------------
  ###

  if (selected_true_methods[true_method] == "MRMix") {
    color.dash <- "black"
  } else if (selected_true_methods[true_method] == "FTO_Wald"){
    color.dash <- "blue"
  } else {
    color.dash <- ggthemes_data$few$colors$Dark[9,2][[1]]
  }
  base_size_theta_plot <- 6

  IVW_BMI_GSD_geom_point_dat <- est_sim %>% 
    select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
    pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
    mutate(theta_sim_numeric = as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")))

  ggplot(IVW_GSD_performance_metrics, aes(x=N, y=IVW_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=color.dash, alpha=0.6, linetype=2, size=0.8)+
    # annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
    #        label= expression( paste("ref: ", theta[X] ))  , 
    #        color= ggthemes_data$few$colors$Dark[9,2][[1]]
    #          )+
    # geom_errorbar(aes(ymin=IVW_GSD_mean-1.96*IVW_GSD_emp_se, ymax=IVW_GSD_mean+1.96*IVW_GSD_emp_se), 
    #               width=3000, # x-axis dimension
    #               position = "dodge")+
    ## ADD rainbow plots
    geom_boxplot(data = IVW_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = IVW_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = IVW_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("IVW estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
                           ))+
    theme_few(base_size_theta_plot) -> IVW_GSD_simplot_thetas

@@

  ggplot(MODE_GSD_performance_metrics, aes(x=N, y=MODE_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=color.dash, alpha=0.6, linetype=2, size=0.8)+
    # geom_errorbar(aes(ymin=MODE_GSD_mean-1.96*MODE_GSD_emp_se, ymax=MODE_GSD_mean+1.96*MODE_GSD_emp_se), 
    #               width=3000, # x-axis dimension
    #               position = "dodge")+
    ## ADD rainbow plots
    geom_boxplot(data = MODE_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = MODE_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = MODE_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("MODE estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
         )
    ) +
    theme_few(base_size_theta_plot) -> MODE_GSD_simplot_thetas

@@

  ggplot(CONMIX_GSD_performance_metrics, aes(x=N, y=CONMIX_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=color.dash, alpha=0.6, linetype=2, size=0.8)+
    ## ADD rainbow plots
    geom_boxplot(data = CONMIX_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = CONMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = CONMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("CONMIX estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
         )
    ) +
    theme_few(base_size_theta_plot) -> CONMIX_GSD_simplot_thetas

@@

  ggplot(MRMIX_GSD_performance_metrics, aes(x=N, y=MRMIX_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=color.dash, alpha=0.6, linetype=2, size=0.8)+
    ## ADD rainbow plots
    geom_boxplot(data = MRMIX_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = MRMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = MRMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("MRMIX estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
         )
    ) +
    theme_few(base_size_theta_plot) -> MRMIX_GSD_simplot_thetas

@@

  ggplot(MEDIAN_GSD_performance_metrics, aes(x=N, y=MEDIAN_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=color.dash, alpha=0.6, linetype=2, size=0.8)+
    ## ADD rainbow plots
    geom_boxplot(data = MEDIAN_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = MEDIAN_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = MEDIAN_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("MEDIAN estimate: BMI -> GSD"
                           #"\nSelected Reference Method: ", 
                           #selected_true_methods[true_method], 
                           #" estimate calculated with total sample size")
         )
    ) +
    theme_few(base_size_theta_plot) -> MEDIAN_GSD_simplot_thetas

@@

  arrangedplot.thetas.all[[true_method]] <- GSD_simplot_thetas_arrange

  if (SAVE.files ==TRUE ){
    filename_GSD_simplot_thetas_arrange <- paste0("./output/plots/theta_sims/", Sys.Date(), "_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".svg")
    ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
           width = 4, height = 14, device = "svg",
           units = "in"  # default
           )
  }

@@

names(arrangedplot.thetas.all) <- selected_true_methods
